Race Science in Mainstream Psychology, 1960-2010

### 2025-04-07 paper/paper.qmd
updating racist agnotology discussion
adding paragraph connecting racist agnotology to norms and practices in psychology

>>>>

Furthermore, the maintenance of doubt or ignorance about race within psychological science can be achieved not just via the explicit race science research of a small minority of psychologists who seek to create that doubt or ignorance in the first place [cf. @WinstonWhyMainstreamResearch2020], but also through the norms and traditions of the discipline that are engaged in by the average psychological scientist. For example, Roberts and Mortensen analyzed over 1700 articles published between 1995 and 2018 in seven psychology journals, finding that research using White samples was more likely than research using samples of color to be presented in race-neutral language [@roberts2023challenging]. They reported this finding in the context of a larger argument about how psychology as a discipline treats White as a default and nonracial description of humanity and offering suggestions for how psychology can move past this longstanding implicit yet discipline-wide framework. The treatment of Whiteness as racially neutral by psychology can, like the reluctance of psychological science organizations to reject racial categories as biologically meaningful, further the goals of those who wish to create racialized ignorance, and it is the responsibility of psychological scientists to rebuke efforts that create ignorance.
